Scientific Report - Summary of Research\\ Ambizione: ``Automatized compilation of sequential software to a diverse set of hardware accelerators''\\ Grant number: PZ00P2 168016\\ Period: 01.05.2018– 31.12.2020\\ Grantee: Tobias Grosser\\ \today

### 2021-04-21 paper.tex
Add referneces
Add a set of publications
Use a short title

\ifx\paperversion\paperversioncamera
  \documentclass[manuscript, nonacm]{acmart}\settopmatter{}
\fi

@@

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption

@@

%% Bibliography style
\bibliographystyle{ACM-Reference-Format}
%% Citation style
%% Note: author/year citations are required for papers published as an
%% issue of PACMPL.
%\citestyle{acmauthoryear}  %% For author/year citations
%\citestyle{acmnumeric}     %% For numeric citations
%\setcitestyle{nosort}      %% With 'acmnumeric', to disable automatic
                            %% sorting of references within a single citation;
                            %% e.g., \cite{Smith99,Carpenter05,Baker12}
                            %% rendered as [14,5,2] rather than [2,5,14].
%\setcitesyle{nocompress}   %% With 'acmnumeric', to disable automatic
                            %% compression of sequential references within a
                            %% single citation;
                            %% e.g., \cite{Baker12,Baker14,Baker16}
                            %% rendered as [2,3,4] rather than [2-4].

@@

%% Title information
\title{Scientific Report - Summary of Research\\
Ambizione: ``Automatized compilation of sequential software to a diverse set of
hardware accelerators''\\
Grant number: PZ00P2 168016\\
Period: 01.05.2018– 31.12.2020\\
Grantee: Tobias Grosser\\
\today
}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.

@@

%% Bibliography
%\bibliography{bibfile}

@@

\subsection{Publications (published)}
\subsection{Publications (accepted)}
\subsection{Publications (in preparation)}

>>>>

\ifx\paperversion\paperversioncamera
  \documentclass[manuscript, nonacm, natbib]{acmart}\settopmatter{}
\fi

@@

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{bibentry}
\nobibliography*

@@

%% Bibliography style
%% Citation style
%% Note: author/year citations are required for papers published as an
%% issue of PACMPL.
%\citestyle{acmauthoryear}  %% For author/year citations
%\citestyle{acmnumeric}     %% For numeric citations
%\setcitestyle{nosort}      %% With 'acmnumeric', to disable automatic
                            %% sorting of references within a single citation;
                            %% e.g., \cite{Smith99,Carpenter05,Baker12}
                            %% rendered as [14,5,2] rather than [2,5,14].
%\setcitesyle{nocompress}   %% With 'acmnumeric', to disable automatic
                            %% compression of sequential references within a
                            %% single citation;
                            %% e.g., \cite{Baker12,Baker14,Baker16}
                            %% rendered as [2,3,4] rather than [2-4].

@@

%% Title information
\title[]{Scientific Report - Summary of Research\\
Ambizione: ``Automatized compilation of sequential software to a diverse set of
hardware accelerators''\\
Grant number: PZ00P2 168016\\
Period: 01.05.2018– 31.12.2020\\
Grantee: Tobias Grosser\\
\today
}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.

@@

@@

\subsection{Publications (published)}
\begin{itemize}
	\item \bibentry{chelini2021mlir}
	\item \bibentry{10.1145/3437801.3441613}
	\item \bibentry{grosser2020fast}
	\item \bibentry{chelini2020automatic}
	\item \bibentry{khan2020polyhedral}
	\item \bibentry{schueki2020llhd}
	\item \bibentry{kurth2020mixed}
	\item \bibentry{kourtis2020compiling}
\end{itemize}
\subsection{Publications (accepted)}
\subsection{Publications (under review)}
\subsection{Publications (in preparation)}
\begin{itemize}
	\item \bibentry{gysi2020ooc}
\end{itemize}

%% Bibliography
\bibliographystyle{plainnat}
\nobibliography{references}
